Synthesizing Symmetric Lenses

### 2018-05-25 papers/SymmetricLenses/main.tex
push a version

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage[inline]{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}

@@

\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3158089}
\acmYear{2018}
\copyrightyear{2018}
\acmJournal{PACMPL}
\acmVolume{2}
\acmNumber{POPL}
\acmArticle{1}
\acmMonth{1}
\startPage{1}

@@

We develop an algorithm that synthesizes a low-cost lens. Our algorithm consists
of two communicating synthesizers, one that proposes candidate stochastic
regular expression pairs that it thinks will align well, and one that greedily
searches for a lens between those two regular expressions that minimizes cost
and involves no rewrites.

Our first algorithm, \TypeProp, proposes candidate stochastic regular
expressions. These candidate stochastic regular expressions are generated by
traversing \emph{star semiring} equivalences on stochastic regular expressions.
These proposed stochastic regular expression pairs have equivalent languages and
probability distributions as the original ones: we prove the star-semiring
rewrites this synthesizer applies are sound rewrites on stochastic regular
expression.

@@

% begin extended example
\section{Extended Example}
We motivate our problem with an extended example.  Consider the previously
described scenario of keeping Linux and Windows scheduled jobs synchronized.
% end extended example

@@

\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\String}{\String'}$
    & =
    & $\begin{cases*}1 & if $\String = \String'$\\ 0 & otherwise\end{cases*}$ \\

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage[inline]{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}

\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}

@@

\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3158089}
\acmYear{2019}
\copyrightyear{2019}
\acmJournal{PACMPL}
\acmVolume{3}
\acmNumber{POPL}
\acmArticle{1}
\acmMonth{1}
\startPage{1}

@@

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic Diagram for \SOptician. Regular expressions \Regex and
    \RegexAlt, and a set of examples \Examples, are provided as input. \RXSearch
    searches through stochastic regular expression pairs, equivalent to the
    originals, and proposes them to \GreedySynth. \GreedySynth finds a lens,
    typed between the generated equivalent pairs. When \RXSearch determines it
    has an optimal lens, it returns that lens.}
  \label{fig:high-level-algorithm}
\end{figure}

We develop an algorithm that synthesizes a low-cost lens, shown in
Figure~\ref{fig:high-level-algorithm}. Our algorithm consists of two
communicating synthesizers, one that proposes candidate stochastic regular
expression pairs that it thinks will align well, and one that greedily searches
for a lens between those two regular expressions that minimizes cost and
involves no rewrites. When the first algorithm thinks it has found the best
possible lens, it returns that lens.

Our first algorithm, \RXSearch, proposes candidate stochastic regular
expressions. These candidate stochastic regular expressions are generated by
traversing \emph{star semiring} equivalences on stochastic regular expressions.
These proposed stochastic regular expression pairs have equivalent languages and
probability distributions as the original ones: we prove the star-semiring
rewrites this synthesizer applies are sound rewrites on stochastic regular
expression.

@@

% begin extended example
\section{Extended Example}

\begin{figure}
  % https://tex.stackexchange.com/questions/168741/showing-two-listings-in-a-table-side-by-side
  \setbox0=\hbox{%
    \begin{minipage}{3in}
\begin{lstlisting}[
tabsize=1,
language={xml},
]
0,20,40 cp -r /Library/ "$\$$(date)"

* df -h | sendmail admin@domain.com
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingA}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3in}
\begin{lstlisting}[
tabsize=1,
]
<Tasks>
 <Task>
  <Command>c</Command>
  <Time>0</Time><Time>20</Time><Time>40</Time>
 </Task>
 <Task>
  <Command>c</Command>
  <AllTimes/>
 </Task>
<Tasks>

{
  Title: Return 400 on
    bad PUT request,
  Type: Bug,
  AssignedTo: J Smith,
}
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingB}{\box0}
  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{lightyellow}}c|>{\columncolor{lightgreen}}c|}
      \hline
      Legacy Work Item Representation & Modern Work Item Representation \\
      \hline
      \listingA & \listingB \\
      \hline
    \end{tabular}
  }
  \caption{Hello there this is the thing}
  \label{fig:minimized-representations}
\end{figure}

We motivate our problem with an extended example.  Consider the previously
described example of keeping Linux and Windows scheduled jobs synchronized.
In this example, we describe keeping synchronized an minified version of
crontab and the task scheduler.  These are each formats specifying when to run
recurring tasks.  For simplicity, we are using an minified version of these
configuration files where we can schedule tasks to occur at fixed intervals,
hourly, daily, or weekly.  Each task consists of a command to be run.

In this example, we wish for the jobs to be synchronized across our windows and
linux devices. However, the commands that need to be run are typically different
for each device. Paths are different in windows and Linux, and while there is
typically a Windows equvialent for Linux commands, that equivalent command is
not always named the same thing.

To synchronize these files, we wish to synchronize how often the commands are
run, but not synchronize the names of the commands. We consider 4 functions to
be necessary to synchronize these two files: a function that makes a new cron
file from a newly created task scheduler, a function that makes a new task
scheduler file from a new cron file, a function that merges edits to the cron
file to the synchronized task scheduler file, and a function that merges edits
on the task scheduler file to the cron file. These are the only four functions
we need to synchronize these two files, so these four functions comprise a
simple symmetric lens between cron files and task scheduler files.  More
formally, a simple symmetric lens between $X$ and $Y$ comprise the following
four functions:
\begin{enumerate}
\item $\CreateR \OfType X \rightarrow Y$
\item $\CreateL \OfType Y \rightarrow X$
\item $\PutR \OfType X \rightarrow Y \rightarrow Y$
\item $\PutL \OfType Y \rightarrow X \rightarrow X$
\end{enumerate}

Furthermore, we expect these functions to satisfy certain properties.  For
example, if two files are synchronized by one of these functions, using another
function to resynchronize it will not change the result.  These are viewed as
the ``round-tripping'' laws:
\vspace*{-1em}
\begin{gather}
  \tag{\CreatePutRL}
  \PutLOf{(\CreateROf{x})}{x} = x\\
  \tag{\CreatePutLR}
  \PutROf{(\CreateLOf{y})}{y} = y\\
  \tag{\PutRL}
  \PutLOf{(\PutROf{x}{y})}{x} = x\\
  \tag{\PutLR}
  \PutROf{(\PutLOf{y}{x})}{y} = y
\end{gather}

\vspace*{-1em}
We wish 
% end extended example

@@

\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\String}{\String''}$
    & =
    & $\begin{cases*}1 & if $\String = \String'$\\ 0 & otherwise\end{cases*}$ \\
